full title

### 2020-11-20 paper/pldi21/eval.tex
Minor fix in Sec. 5

We evaluated our tool based on the following research questions:
\begin{itemize}
  \item \textbf{RQ1) Analysis Speed-up:} How much analysis time is reduced by
    adding dynamic shortcut to static analysis?
  \item \textbf{RQ2) Precision Improvement:} How much analysis precision is
    improved by replacing the manual modeling with dynamic shortcut?
  \item \textbf{RQ3) Opaque Function Coverage:} How many opaque functions are
    covered by dynamic shortcut without using manual modeling?
\end{itemize}
We targeted the official 306 tests of Lodash 4
(v.4.17.20)\footnote{https://github.com/lodash/lodash/blob/4.17.20/test/test.js}
used in motivating examples (Section~\ref{sec:motivation}).  The most recent
papers for JavaScript static analysis techniques~\cite{value-refinement,
value-partitioning} also evaluated their techniques based on them.
Among them, we filtered out \inred{37} tests including JavaScript language
features SAFE does not support, such as dynamic code generation using
\jscode{Function}, getter/setter, and browser specific features
(e.g. $\jscode{__proto__}$).  Thus, we only targeted \inred{269} out of 306
tests for the evaluation.  We performed our experiments on an Ubuntu machine
equipped with 4.2GHz Quad-Core Intel Core i7 and 64GB of RAM.

@@

To evaluate the effectiveness of the dynamic shortcut, we performed static
analysis for \inred{269} Lodash 4 tests with and without dynamic shortcut.
Figure~\ref{fig:conc-analysis-time} depicts the histogram for their analysis
time and the box plot for speed up after applying the dynamic shortcut.  While
the base analysis (no-DS) finished \inred{199} out of \inred{269} tests within 5
minutes, our tool finished all tests with the dynamic shortcut (DS).  For
\inred{199} tests analyzable by both analyses, the analysis took \inred{168.4}
seconds and \inred{12.2} seconds on average without dynamic shortcut (no-DS) and
with dynamic shortcut (DS), and the dynamic shortcut accelerates
\inred{20.16}\textsf{x} the static analysis on average.  Only for one test using
$\jscode{_.sample}$ (a Lodash 4 library that randomly samples a value from a
given array), the static analysis using dynamic shortcut had
\inred{0.81}\textsf{x} speed of the base analysis because of the frequent use of
dynamic shortcut (\inred{24} times).

>>>>

We evaluated our tool based on the following three research questions:
\begin{itemize}
\item \textbf{RQ1) Analysis Speed-up:} How much analysis time is reduced by
using dynamic shortcuts during static analysis?
\item \textbf{RQ2) Precision Improvement:} How much analysis precision is
improved by using dynamic shortcuts instead of manual modeling?
\item \textbf{RQ3) Opaque Function Coverage:} How many opaque functions are
covered by dynamic shortcuts without using manual modeling?
\end{itemize}
We selected the official 306 tests of Lodash 4
(v.4.17.20)\footnote{https://github.com/lodash/lodash/blob/4.17.20/test/test.js}
used in the motivating examples in Section~\ref{sec:motivation} as our evaluation target.
The most recent papers about JavaScript static analysis techniques~\cite{value-refinement,
value-partitioning} also used the tests to evaluate their techniques.
Among them, we filtered out \inred{37} tests that use JavaScript language
features SAFE does not support such as dynamic code generation using
\jscode{Function}, getters and setters, and browser-specific features like $\jscode{__proto__}$.
Thus, we used \inred{269} out of 306 tests for the evaluation of $\tool$.
We performed our experiments on a Ubuntu machine
equipped with 4.2GHz Quad-Core Intel Core i7 and 64GB of RAM.

@@

To evaluate the effectiveness of using dynamic shortcuts, we performed static
analysis of \inred{269} Lodash 4 tests with and without dynamic shortcuts.
%
Figure~\ref{fig:conc-analysis-time} depicts the histogram for their analysis
time and the box plot for speed up after applying the dynamic shortcut.  While
the base analysis (no-DS) finished \inred{199} out of \inred{269} tests within 5
minutes, our tool finished all tests with the dynamic shortcut (DS).  For
\inred{199} tests analyzable by both analyses, the analysis took \inred{168.4}
seconds and \inred{12.2} seconds on average without dynamic shortcut (no-DS) and
with dynamic shortcut (DS), and the dynamic shortcut accelerates
\inred{20.16}\textsf{x} the static analysis on average.  Only for one test using
$\jscode{_.sample}$ (a Lodash 4 library that randomly samples a value from a
given array), the static analysis using dynamic shortcut had
\inred{0.81}\textsf{x} speed of the base analysis because of the frequent use of
dynamic shortcut (\inred{24} times).
